\documentclass[11pt]{report}

\usepackage{epsf,amsmath,amsfonts}
\usepackage{graphicx}
\usepackage{listings}
\usepackage{color}

\setlength{\topmargin}{0in}
\setlength{\headheight}{0in}
\setlength{\headsep}{0in}
\setlength{\textheight}{9.0in}
\setlength{\textwidth}{6.0in}
\setlength{\evensidemargin}{0.25in}
\setlength{\oddsidemargin}{0.25in}

\definecolor{gray}{rgb}{0.4,0.4,0.4}
\definecolor{darkblue}{rgb}{0.0,0.0,0.6}
\definecolor{cyan}{rgb}{0.0,0.6,0.6}

\lstset{
	basicstyle=\ttfamily,
		columns=fullflexible,
		showstringspaces=false,
		commentstyle=\color{gray}\upshape
}

\lstdefinelanguage{XML}
{
	morestring=[b]",
	morestring=[s]{>}{<},
	morecomment=[s]{<?}{?>},
	stringstyle=\color{black},
	identifierstyle=\color{darkblue},
	keywordstyle=\color{cyan},
	morekeywords={xmlns,version,type,name,type,dimensions,name\_in\_code,units,description,template,streams,persistence}% list your attributes here
}

\begin{document}

\title{Framework Testing Core: \\
Requirements and Design}
\author{MPAS Development Team}

\maketitle
\tableofcontents

%-----------------------------------------------------------------------

\chapter{Summary}

Presently MPAS lacks a robust testing mechanism for a lot of the capabilities
that framework and operators provide. This document introduces the concept of a
framework testing core. This core is intended to function only based on the
union of all of the other cores (i.e. things that are deemed required by all
other cores). The purpose of this core is to exercise shared parts of MPAS, and
provide reassuance to the developer/user community that those parts of MPAS are
functioning properly.

%-----------------------------------------------------------------------

\chapter{Requirements}

To support the growing framework and operators code bases within MPAS, the
framework testing core capabilities in MPAS must meet the following
requirements.

\begin{enumerate}

\item MPAS must provide a framework testing core that may run using any mesh
	  that can be input into any MPAS core. This means the core must only take as
	  input variables which are required by all other cores.

\item MPAS must provide testing routines to exercise the shared parts of the
      MPAS code base. Namely framework and operators.

\item Tests must be built in such a way that there is a clear pass/fail metric.

\end{enumerate}                                                             


%-----------------------------------------------------------------------

\chapter{Design and Implementation}
\chapter{Testing}
\end{document}
